Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-30 paper/introduction.tex
footnote

The BGP configurations produced by our compiler are
guaranteed to be policy-compliant in the face of
{\em arbitrary} failures. This does not mean that the implementation is always 
able to send traffic to its ultimate destination 
(\EG in the case of a network partition), but rather that it always respects the 
centralized policy, which may include dropping traffic when there is no route.
%
In this way, we provide network operators
with a strong guarantee that is otherwise impossible to achieve
today.
However, some policies simply cannot be implemented correctly in BGP in
 the presence of arbitrary failures.  We develop new
algorithms to detect such policies
and report our findings to the operators, so they may fix the policy
specification at compile time rather than experience undesirable
behavior after the configurations are deployed.
%We also analyze route aggregation to detect the possibility of failure-induced black-holes.

>>>>

The BGP configurations produced by our compiler are
guaranteed to be policy-compliant in the face of
{\em arbitrary} failures.\footnote{The control plane of a network may use more than one routing protocol, e.g., an IGP in addition to BGP. We assume that these other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
able to send traffic to its ultimate destination
(\EG in the case of a network partition), but rather that it always respects the
centralized policy, which may include dropping traffic when there is no route.
%
In this way, we provide network operators
with a strong guarantee that is otherwise impossible to achieve
today.
However, some policies simply cannot be implemented correctly in BGP in
 the presence of arbitrary failures.  We develop new
algorithms to detect such policies
and report our findings to the operators, so they may fix the policy
specification at compile time rather than experience undesirable
behavior after the configurations are deployed.
%We also analyze route aggregation to detect the possibility of failure-induced black-holes.
